Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-07-31 latex/prelims.tex
Intro ready

\subsection{Forward Problems}\label{subsec:abstract OED}
In this section we give definitions and notations for forward problems,
which are an essential part of the inverse problems we discuss
later. Consider a "parameter space" \(\hilp\) and an "observation
space" \(\hilo\) --- both separable Hilbert spaces (the subscripts p
and o are for "parameter" and "observation", respectively). The
parameter space includes the quantity we seek to infer; in the inverse
problem of the heat equation, the parameter space $\hilp$ is where the
initial condition lives. The observation space $\hilo$, on the other
hand, is the space from which we take measurements; in the example of
the 1D heat equation, $u(\cdot, T) \in \hilo$.

@@

\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps) (\obs \eps' +
      \eps)^t ]
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I_m , 
  \end{split}
\end{align}
where
\begin{align}\label{eq:modcov explained}
  \begin{split}
    [\obs \modcov \obs^*]_{ij} & = e_i^t \obs \modcov \obs^* e_j 
    %
    %
    %
    = \meas_i (\modcov \meas_j).% \text{ (by \eqref{eq:obs*})}.
  \end{split}
\end{align}
Taking \(\modcov = 0\) is a common practice
\cite{tarantola2005,kaipio2005,Vogel02} and then \(\Sigma =
\sigma^2I_m\) is a scalar matrix which does not depend on \(\obs\).

\subsection{Bayesian Linear Inverse Problems}\label{subsec:bayesian inverse problems}
In the previous section, we saw how a parameter $u\in \hilp$ is
transported to the observation space via the forward operaror $\fwd u
\in \hilo$, how observations are generated from a parameter via $\obs
\fwd u$ and how observations and noise give rise to data $\data$. It
is time to formulate the process of inferring the parameter as a
Bayesian inverse problem. The first ingredient we need is a prior.

We take a Gaussian prior \(\param \sim \pr = \normal(\prmean
,\prcov)\) with some appropriate covariance operator \(\prcov\) on
\(\hilp\) \cite{Stuart10}. For example, for the inverse problem of the
1D heat equation we chose $\prcov = -\Delta^{-1}$ --- see Section
\ref{subsec:toy}. Note that \(\fwd \prcov \fwd^*\) is the prior
covariance in \(\hilo\) \cite{Stuart10}, and as such is assumed
invertible --- an assumption which we will use later (if \(\fwd\) has
a nontrivial kernel we utilize Occam's Razor and ignore said kernel
altogether).

@@

%% It is important to note that since \(\obs\) is finite-rank,
%% \(\prcov^{1/2} \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}\) is
%% trace-class.
\begin{definition}\label{def:d optimality}
  We say \(\opt\) is \emph{D-optimal} if \(\opt =
  \argmax_{\obs} \tar(\obs)\), where entries of \(\obs \in (\hilo^*)^m\)
  are constrained to some allowed set of measurements in \(\hilo^*\).
\end{definition}

Intuition for Theorem \ref{thm:d optimality} can be gained by
recalling from Section \ref{subsec:D} that for a Bayesian linear model
in finite dimensions, with Gaussian prior and Gaussian noise, a
D-optimal design minimizes the determinant of the posterior covariance
matrix. Theorem
\ref{thm:d optimality} and Definition \ref{def:d optimality} carry a
similar intuition:
\begin{align*}
  \begin{split}
    \tar(\obs) &= \frac12 \log \det ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}) \text{ by \eqref{eq:objective}}\\
    &= \frac12 \log \det \Big( \prcov ( \prcov^{-1} + \fwd ^* \obs^* \Sigma^{-1} \obs \fwd) \Big )\\
    &= \frac12 \log \det \prcov \postcov^{-1} \text{ by \eqref{eq:postcov}}.
    %%  &= \frac12 \log \det \prcov -\frac12 \log \det \postcov.
  \end{split}
\end{align*}
We think of \(\prcov\) as constant, in the sense that $\prcov$ does
not depend on data $\data$. Thus, a D-optimal design minimizes a
quantity analogous to the posterior covariance determinant, similarly
to the finite-dimensional case.

@@

%% \subsection{Sequential vs Simultaneous Optimization}\label{subsec:seq vs sim}
%% From defintion \ref{def:d optimality} we wish to characterize solution(s) of the
%% following optimization problem for \(\tar$. %%: (\hilo^*)^m \to \R$:
%% \begin{align}\label{eq:optimization}
%%   \obs^{\star} := \argmax_{\obs} \tar( \obs ) 
%%   = \argmax_{\obs} \frac12 \log \det 
%%   (I + \prcov^{1/2} \fwd^*\obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}),
%% \end{align}
%% where \(\obs\) is constrained to some allowed set of observations. We
%% call this problem ``simultaneous optimization'', since all
%% observations are decided on simulatneously.

%% For computational reasons, one may prefer to find the best
%% observations in a sequential manner. Denote
%% \begin{equation}\label{eq:def obs_k}
%%   \obs_k := (\meas_1,\dots, \meas_k)^t,  k\leq m.
%% \end{equation}
%% Sequential optimal design proceeds as follows. Find \(\meas_1\) by
%% maximizing \(\tar(\obs_1)$. Then, keeping \(\meas_1\) fixed --- find
%% \(\meas_2\) as the maximizer of \(\tar(\obs_2)$. Then, find \(\meas_3\) by
%% keeping \(\meas_1,\meas_2\) fixed and taking \(\meas_3\) as the maximizer
%% of \(\tar(\obs_3)$. Continue this way until \(\obs_m = \obs\) is
%% found, where \(m\) is the number of available observations. %% It is
%% %% important to notice that this scheme does not require actually
%% %% observing data --- in \eqref{eq:objective} data is averaged out.

%% The analysis in this paper is conducted for the general simultaneous
%% optimization case. The sequential optimization case is dealt with in
%% section \ref{subsec:clusterization sequential}. It is important to
%% note, however that all conclusions we arrive at for the simultaneous
%% case easily specialize to the sequential case by considering the
%% posterior as the next sequential step's prior.

>>>>

\subsection{Forward Problems}\label{subsec:abstract_OED}
In this section we give definitions and notations for forward problems,
which are an essential part of the inverse problems we discuss
later. Consider a "parameter space" \(\hilp\) and an "observation
space" \(\hilo\) --- both separable Hilbert spaces (the subscripts p
and o are for "parameter" and "observation", respectively). The
parameter space includes the quantity we seek to infer; in the inverse
problem of the heat equation, the parameter space $\hilp$ is where the
initial condition lives. The observation space $\hilo$, on the other
hand, is the space from which we take measurements; in the example of
the 1D heat equation, $u(\cdot, T) \in \hilo$.

@@

\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps) (\obs \eps' +
      \eps)^t ]
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I_m , 
  \end{split}
\end{align}
where
\begin{align}\label{eq:modcov_explained}
  \begin{split}
    [\obs \modcov \obs^*]_{ij} & = e_i^t \obs \modcov \obs^* e_j 
    %
    %
    %
    = \meas_i (\modcov \meas_j).% \text{ (by \eqref{eq:obs*})}.
  \end{split}
\end{align}
Taking \(\modcov = 0\) is a common practice
\cite{tarantola2005,kaipio2005,Vogel02} and then \(\Sigma =
\sigma^2I_m\) is a scalar matrix which does not depend on \(\obs\).

\subsection{Bayesian Linear Inverse Problems}\label{subsec:bayesian_inverse_problems}
In the previous section, we saw how a parameter $u\in \hilp$ is
transported to the observation space via the forward operaror $\fwd u
\in \hilo$, how observations are generated from a parameter via $\obs
\fwd u$ and how observations and noise give rise to data $\data$. It
is time to formulate the process of inferring the parameter as a
Bayesian inverse problem. The first ingredient we need is a prior.

We take a Gaussian prior \(\param \sim \pr = \normal(\prmean
,\prcov)\) with some appropriate covariance operator \(\prcov\) on
\(\hilp\) \cite{Stuart10}. For example, for the inverse problem of the
1D heat equation we chose $\prcov = (-\Delta)^{-1}$ --- see Section
\ref{subsec:toy}. Note that \(\fwd \prcov \fwd^*\) is the prior
covariance in \(\hilo\) \cite{Stuart10}, and as such is assumed
invertible --- an assumption which we will use later (if \(\fwd\) has
a nontrivial kernel we utilize Occam's Razor and ignore said kernel
altogether).

@@

%% It is important to note that since \(\obs\) is finite-rank,
%% \(\prcov^{1/2} \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}\) is
%% trace-class.
\begin{definition}\label{def:d_optimality}
  We say \(\opt\) is \emph{D-optimal} if \(\opt =
  \argmax_{\obs} \tar(\obs)\), where entries of \(\obs \in (\hilo^*)^m\)
  are constrained to some allowed set of measurements in \(\hilo^*\).
\end{definition}

Intuition for Theorem \ref{thm:d_optimality} can be gained by
recalling from Section \ref{subsec:D} that for a Bayesian linear model
in finite dimensions, with Gaussian prior and Gaussian noise, a
D-optimal design minimizes the determinant of the posterior covariance
matrix. Theorem
\ref{thm:d_optimality} and Definition \ref{def:d_optimality} carry a
similar intuition:
\begin{align*}
  \begin{split}
    \tar(\obs) &= \frac12 \log \det ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}) \text{ by \eqref{eq:objective}}\\
    &= \frac12 \log \det \Big( \prcov ( \prcov^{-1} + \fwd ^* \obs^* \Sigma^{-1} \obs \fwd) \Big )\\
    &= \frac12 \log \det \prcov \postcov^{-1} \text{ by \eqref{eq:postcov}}.
    %%  &= \frac12 \log \det \prcov -\frac12 \log \det \postcov.
  \end{split}
\end{align*}
We think of \(\prcov\) as constant, in the sense that $\prcov$ does
not depend on data $\data$. Thus, a D-optimal design minimizes a
quantity analogous to the posterior covariance determinant, similarly
to the finite-dimensional case.

@@

%% \subsection{Sequential vs Simultaneous Optimization}\label{subsec:seq_vs_sim}
%% From defintion \ref{def:d_optimality} we wish to characterize solution(s) of the
%% following optimization problem for \(\tar$. %%: (\hilo^*)^m \to \R$:
%% \begin{align}\label{eq:optimization}
%%   \obs^{\star} := \argmax_{\obs} \tar( \obs ) 
%%   = \argmax_{\obs} \frac12 \log \det 
%%   (I + \prcov^{1/2} \fwd^*\obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}),
%% \end{align}
%% where \(\obs\) is constrained to some allowed set of observations. We
%% call this problem ``simultaneous optimization'', since all
%% observations are decided on simulatneously.

%% For computational reasons, one may prefer to find the best
%% observations in a sequential manner. Denote
%% \begin{equation}\label{eq:def_obs_k}
%%   \obs_k := (\meas_1,\dots, \meas_k)^t,  k\leq m.
%% \end{equation}
%% Sequential optimal design proceeds as follows. Find \(\meas_1\) by
%% maximizing \(\tar(\obs_1)$. Then, keeping \(\meas_1\) fixed --- find
%% \(\meas_2\) as the maximizer of \(\tar(\obs_2)$. Then, find \(\meas_3\) by
%% keeping \(\meas_1,\meas_2\) fixed and taking \(\meas_3\) as the maximizer
%% of \(\tar(\obs_3)$. Continue this way until \(\obs_m = \obs\) is
%% found, where \(m\) is the number of available observations. %% It is
%% %% important to notice that this scheme does not require actually
%% %% observing data --- in \eqref{eq:objective} data is averaged out.

%% The analysis in this paper is conducted for the general simultaneous
%% optimization case. The sequential optimization case is dealt with in
%% section \ref{subsec:clusterization_sequential}. It is important to
%% note, however that all conclusions we arrive at for the simultaneous
%% case easily specialize to the sequential case by considering the
%% posterior as the next sequential step's prior.

### 2024-07-31 latex/refs.tex
Intro ready

\documentclass{amsart}
\input{definitions}

@@

@@

\answer: I appreciate the many thoughtful comments by yourself, the
associate editor and the reviewers. I also appreciate the option to
improve the paper. Please see my answers below in blue.

\begin{description}
  \item[a] the Introduction is to be made accessible to the whole BA
    readership;
    \answer: I have considerably extended the introduction.

  \item[b] the motivation and the practical statistical implications are to be
    developed and discussed;
    \answer: I added a section on the implications in the introduction.

  \item[c] the contribution has to be better contextualized with
    respect to the literature in both inverse problems and D-optimal
    designs;
  \answer:

@@

    \answer: I added a section describing numerical experiments and
    their results. I also added documentation to the accompanying
    \href{https://github.com/yairdaon/OED}{repository} and made sure
    all scripts there run.

@@

    \answer: I am not sure which specific comment of Reviewer 3 this
    refers to, please see my answers to Reviewer 3 below.
\end{description}

@@

\answer: I have added considerably to the introduction. See revised
manuscript and diff file.

@@

\answer: I appreciate the kind words.

@@

\answer: If I understand correctly --- I completely agree. I added
text emphasizing that I do not endorse using correlated errors.

Since the author proves the clusterization issue under the independent
measurement assumption, I expect the author to go deeper and explain
why an ordinary data generation assumption + a common optimal design
leads to a “suboptimal” design?
\answer: Aagain, my apologies for the misunderstanding.

@@

\answer: Bla

@@

\answer: I appreciate the comment, I fixed the relevant line in the
manuscript.

@@

\answer: I do not view clusterization as an undesired property, I only
mentioned many authors consider it to be undesirable. I have added a
section contrasting repetition and replication with clusterization and
why I believe they may be different.

@@

\answer: I believe that even in an application where repeated
experiments are allowed they may be unintuitive. For example, in a
medical imaging application --- taking a repeated slice in an MRI scan
might seem suboptimal to some. Of course, there is no argument
regarding the optimality give a model, which, as you mention might be
wrong.

@@

\answer: I believe clusterization may imply a model is somehow in
adequate, see text below.

@@

\answer: I couldn't agree more. Indeed, the suboptimality of clustered
design is a matter of personal opinion; once a design criterion and a
model are agreed upon there can be no disagreement.

@@

  \answer: I do consider experiments where repeated measurements are
  possible. I am giving insight on why such designs are useful, even
  though repeated measurements may be non-intuitive in certain
  settings.

@@

  \answer: great comment
\end{enumerate}

@@

\answer: Thanks for this comment. I considerably expanded the
introduction and delegated many proofs to the Supplementary. I also
added a section on practical implications, reproduced below.

@@

\answer: To a certain extend I agree: indeed, the impossibility of
taking identical measurements is indeed natural. However, this is not
encoded in the mathematical formulation of the problem. One can then
take one of two approaches: either accept what the mathematics
suggest, even if it counterintuitive, or find ways to circumvent the
mathematics because the result seems non-intuitive.

Secondly, the paper seems to suggest “imposing correlations between
observations” as a solution. However, isn’t this imposition pragmatic
as well? I suppose it is argued that the $\obs \eps′$ term is
accounting for model error: but it is still pragmatic: the data
acquisition given by equation (1) is not the true data-generating
process.

\answer: I do not support imposing correlations in the paper, I just
used correlations to show how my framework can be used to rigorously
prove what is widely accepted. Other referees also understood that the
paper endorses imposing correlations and I accept that this is my
error in writing. I added a clause clearing the issue.

@@

  \answer: I changed $\obs^\star$ to $\opt$.

@@

  \answer: I was not able to find a better term to replace
  "measurements", so I stuck to it.

@@

  \answer: Absolutely correct, I changed it to $\nu$. You will not
  find the revised proof in the manuscript since I moved it to the
  Supplementray.
\end{itemize}

@@

\answer: I apologize for not properly maintainig the repository. It is
now functioning and well-documented.

@@

\answer: I appreciate the suggestion. I added a section on numerical
simulations to the main atricle. It is reproduced below.

@@

  \answer: It is impossible to visually discern the measurements, even
  when resolution is increased. These measurements are not identical
  numerically, but they are identical to five decimal digits. Since I
  find these points via optimization over point location in
  $\Omega=[0,1]$ I view an error $<10^{-5}$ as reasonable.

@@

  \answer: That is a great point!

\item Further, a dimensionality effect should also arise directly from
  Theorem 1 via the prior covariance eigenvalues: in the experiment
  the prior covariance operator is set to be equal to the inverse
  Laplace operator $(−\Delta)^{−1}$ . In d-dimensional domains, its
  eigenvalues $\lambda_j$ are known to follow Weyl’s asymptotics,
  growing as $j^{2/d}$, which should then impact the index after
  which the eigenvalues are ‘thresholded’ by the procedure.

@@

  \answer: I added relevant simulations to a new section Numerical
  Experiments.

@@

  \answer: I removed the statement of Theorem 1 from the introudction.

@@

  \answer: Thank you for the comment, I completely agree. Optimal
  designs are now denoted $\opt$.

@@

  \answer: I am glad you view this part as unnecessary, but I feel the
  model might feel too abstract to some practitioners. Thus, I choose
  to keep this part to avoid complaints from other readers.

@@

  \answer: Basically I meant that its eigenvalues decrease
  "quickly". I understand this is not a commot or well-defined term so
  I removed the relevant sentence.

@@

  \answer: Great comment! Such cases are possible but I view them as
  pathological. See short paragraph below.

@@

  \answer: I do not expect this conclusion to hold: if noise is
  present, any measurement will result in some information gain and an
  increase in design criterion.

@@

  \answer: I believe a posterior can be defined, and so a KL
  divergence from said posterior to prior could be calculated and
  $\tar$ evaluated. However, taking $\sigma = 0$ in the main theorem
  implies $\tar \equiv \infty$. I believe this is because do not know
  how to mitigate this

@@

  \answer: the Matern-like prior actually arises by using a
  Laplacian-like operator as a prior, see Rue and Lindgren \cite{}. So
  a study of this example (with and without correlated errors) is
  already included in the paper. I am afraid implementing another
  inverse problem is out of scope for the present paper since I was
  not able to install common packages for inverse problems on my machine.

@@

  \answer: Indeed, point evaluations $\delta_x$ are not in any
  function space I consider in the paper since my analysis is limited
  to Hilbert spaces. Point evaluations can be approximated well,
  though so in my opinion this is not a deal breaker. The only caveat
  is that upon approximating point evaluations e.g.~by $R(x;t) =
  t\mathbb{1}_{-t/2, t/2}(x)$ we will need to change the norm
  constraints to the norsomething different (i.e.~$\|R(\cdot;t\|$) but
  that does not change the analysis. I skim over this issue in the
  paper since I think it is confusing and adds little context.

@@

  \answer: I explain this in more detail in the paper. See text below.

>>>>

\documentclass{amsart}
\input{definitions}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}

\newcommand{\paste}[1]{\vskip 0.05in \textcolor{red}{#1}\vskip 0.05in}
\newcommand{\answer}[1]{\vskip 0.05in \textcolor{blue}{#1} \vskip 0.05in}

@@

I appreciate the many thoughtful comments by all of you. I believe
these comments helped me considerably improve the exposition of my
paper and added new insights as well. I sincerely appreciate the
option to revise and resubmit. Please see below my answers to the
comments made by the referees, associate editor and editor in chief:
\answer{My answers are marked in blue.} \paste{In some places I
  copied text from the revised manuscipt and marked it in red.}

@@

\begin{description}
  \item[a] the Introduction is to be made accessible to the whole BA
    readership;
    \answer{I have considerably extended the introduction.}

  \item[b] the motivation and the practical statistical implications
    are to be developed and discussed;

    \answer{I added a section on the implications in the
      introduction.}

  \item[c] the contribution has to be better contextualized with
    respect to the literature in both inverse problems and D-optimal
    designs;
  \answer{adfasd}

@@

    \answer{I added a section describing numerical experiments and
    their results. I also added documentation to the accompanying
    \href{https://github.com/yairdaon/OED}{repository} and made sure
    all scripts there run.}

@@

    \answer{I am not sure which specific comment of Reviewer 3 this
    refers to, please see my answers to Reviewer 3 below. }
\end{description}

@@

\answer{I have added considerably to the introduction. See revised
manuscript and diff file.}

@@

\answer{I appreciate the kind words.}

@@

\answer{If I understand correctly --- I completely agree. I added
text emphasizing that I do not endorse using correlated errors:}
\paste{asdf}

Since the author proves the clusterization issue under the independent
measurement assumption, I expect the author to go deeper and explain
why an ordinary data generation assumption + a common optimal design
leads to a “suboptimal” design?
\answer{Aagain, my apologies for the misunderstanding.}

@@

\answer{Bla }

@@

\answer{I appreciate the comment, I fixed the relevant line in the
manuscript.}

@@

\answer{I do not view clusterization as an undesired property, I only
mentioned many authors consider it to be undesirable. I have added a
section contrasting repetition and replication with clusterization and
why I believe they may be different. }

@@

\answer{I believe that even in an application where repeated
experiments are allowed they may be unintuitive. For example, in a
medical imaging application --- taking a repeated slice in an MRI scan
might seem suboptimal to some. Of course, there is no argument
regarding the optimality give a model, which, as you mention might be
wrong.}

@@

\answer{I believe clusterization may imply a model is somehow
  inadequate, see text below. }

@@

\answer{I couldn't agree more. Indeed, the suboptimality of clustered
design is a matter of personal opinion; once a design criterion and a
model are agreed upon there can be no disagreement.}

@@

  \answer{I do consider experiments where repeated measurements are
  possible. I am giving insight on why such designs are useful, even
  though repeated measurements may be non-intuitive in certain
  settings.}

@@

  \answer{great comment}
\end{enumerate}

@@

\answer{Thanks for this comment. I considerably expanded the
introduction and delegated many proofs to the Supplementary. I also
added a section on practical implications, reproduced below.}

@@

\answer{To a certain extend I agree: indeed, the impossibility of
taking identical measurements is indeed natural. However, this is not
encoded in the mathematical formulation of the problem. One can then
take one of two approaches: either accept what the mathematics
suggest, even if it counterintuitive, or find ways to circumvent the
mathematics because the result seems non-intuitive.}

Secondly, the paper seems to suggest “imposing correlations between
observations” as a solution. However, isn’t this imposition pragmatic
as well? I suppose it is argued that the $\obs \eps'$ term is
accounting for model error: but it is still pragmatic: the data
acquisition given by equation (1) is not the true data-generating
process.

\answer{I do not support imposing correlations in the paper, I just
used correlations to show how my framework can be used to rigorously
prove what is widely accepted. Other referees also understood that the
paper endorses imposing correlations and I accept that this is my
error in writing. I added a clause clearing the issue.}

@@

  \answer{I changed $\obs^\star$ to $\opt$.}

@@

  \answer{I was not able to find a better term to replace
  "measurements", so I stuck to it.}

@@

  \answer{Absolutely correct, I changed it to $\nu$. You will not
  find the revised proof in the manuscript since I moved it to the
  Supplementray.}
\end{itemize}

@@

\answer{I apologize for not properly maintainig the repository. It is
  now functioning and well-documented.}

@@

\answer{I appreciate the suggestion. I added a section on numerical
simulations to the main atricle. It is reproduced below.}

@@

  \answer{It is impossible to visually discern the measurements, even
  when resolution is increased. These measurements are not identical
  numerically, but they are identical to five decimal digits. Since I
  find these points via optimization over point location in
  $\Omega=[0,1]$ I view an error $<10^{-5}$ as reasonable.}

@@

  \answer{That is a great point, but I view experiments in higher
    dimension as out of scope for the current study.}

\item Further, a dimensionality effect should also arise directly from
  Theorem 1 via the prior covariance eigenvalues: in the experiment
  the prior covariance operator is set to be equal to the inverse
  Laplace operator $(-\Delta)^{-1}$. In d-dimensional domains, its
  eigenvalues $\lambda_j$ are known to follow Weyl’s asymptotics,
  growing as $j^{2/d}$, which should then impact the index after which
  the eigenvalues are ‘thresholded’ by the procedure.

  \answer{Indeed, the growth of eigenvalues of the Laplacian is
    different in higher dimensions. This is why in higher dimensions
    we would have to take as prior \(u_0 \sim \mathcal{N}(\param_0,
    (-\Delta)^{-\gamma})\), for some \(\gamma > d/2\) in order to
    maintain regularity of prior realizations. I decided not to
    include a discussion on the choice of priors in higher spatial
    dimensions because it would require too much exposition and make
    me digress from the main points I wanted to convey, see the
    relevant paragraph below:}
  \paste{We choose a prior for the initial condition $u_0 \sim \mathcal{N}(0,
    (-\Delta)^{-1})$, with homogeneous Dirichlet boundary condition. This
    choice ensures the posterior is well-defined and prior realizations
    are well-behaved, see \cite[Theorem 3.1 and Lemma 6.25]{Stuart10} for
    details.}

@@

  \answer{I added relevant simulations to a new section Numerical
  Experiments.}

@@

  \answer{I removed the statement of Theorem 1 from the introudction.}

@@

  \answer{Thank you for the comment, I completely agree. Optimal
  designs are now denoted $\opt$.}

@@

  \answer{I am glad you view this part as unnecessary, but I feel the
  model might feel too abstract to some practitioners. Thus, I choose
  to keep this part to avoid complaints from other readers.}

@@

  \answer{Basically I meant that its eigenvalues decrease
    "quickly". I understand this is not a common or well-defined term
    so I removed the relevant sentence.}

@@

  \answer{Great comment! Such cases are possible but I view them as
  pathological. See short paragraph below.}

@@

  \answer{I do not expect this conclusion to hold: if noise is
  present, any measurement will result in some information gain and an
  increase in design criterion.}

@@

  \answer{I believe a posterior can be defined, and so a KL
  divergence from said posterior to prior could be calculated and
  $\tar$ evaluated. However, taking $\sigma = 0$ in the main theorem
  implies $\tar \equiv \infty$. I believe this is because do not know
  how to mitigate this}

@@

  \answer{the Matern-like prior actually arises by using a
  Laplacian-like operator as a prior, see Rue and Lindgren \cite{}. So
  a study of this example (with and without correlated errors) is
  already included in the paper. I am afraid implementing another
  inverse problem is out of scope for the present paper since I was
  not able to install common packages for inverse problems on my machine. }

@@

  \answer{Indeed, point evaluations $\delta_x$ are not in any
  function space I consider in the paper since my analysis is limited
  to Hilbert spaces. Point evaluations can be approximated well,
  though so in my opinion this is not a deal breaker. The only caveat
  is that upon approximating point evaluations e.g.~by $R(x;t) =
  t\mathbb{1}_{-t/2, t/2}(x)$ we will need to change the norm
  constraints to the norsomething different (i.e.~$\|R(\cdot;t\|$) but
  that does not change the analysis. I skim over this issue in the
  paper since I think it is confusing and adds little context.}

@@

  \answer{I explain this in more detail in the paper. See text below.}
